---
title: "ChIP-Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset 

Dataset is a subsuet of the lymphoblastoid cell line
 GM12878 from the ENCODE project Consortium 2012. 
 Dataset is mapped to GRCh38 the hg38 version of human genome. 
 Data is retrieved from the compGenomeRData package. 

###  load data 

The data has two ChIP experiments:
*Transcription factors : CTCF, SMC3, ZNF143, and RNA polymerase 2.
*Histone modifications H3K4me3,H3K36me3 , H3K27ac, H3K273me
*Input data 

```{r}

#define data path 
data_path = system.file("extdata/chip-seq", package = "compGenomRData")

#list the number of files in data 
chip_files = list.files(data_path,full.names = TRUE)
chip_files

```
## Quality Control of ChIP Data

the objective is to determine read quality 
and if the chromatin immunoprecipitation enrichment 
exerpiment was successful. There are four steps in 
ChIP quality control;
1. sample correlation clustering 
2. Data visualization 
3. Average fragment length determination 
4. Visualization of GC bias. 

#1 Sample Correlation Clustering 

##Load libraries 
```{r}
library(GenomeInfoDb)
library(compGenomRData)
library(tidyverse)
```


```{r}
hg_chrs = getChromInfoFromUCSC('hg38')
hg_chrs
```
